Recursive Neural Network Part-of-Speech Tagger

### 2013-12-20 paper/paper.tex
Add all our references.

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

>>>>

\bibitem[\protect\citename{Collobert and Weston}2011]{Collobert:11}
Ronan~Collobert, Jason~Weston, Léon~Bottou, Michael~Karlen, Koray~Kavukcuoglu and Pavel~Kuksa.
\newblock 2011.
\newblock Natural Language Processing (Almost) from Scratch.
\newblock {\em Journal of Machine Learning Research 12},  (2011) 2461-2505.
\newblock The MIT Press, Cambridge, MA.

\bibitem[\protect\citename{Collobert, Kavukcuoglu and Farabet}2011]{Collobert:11}
Ronan~Collobert, Koray~Kavukcuoglu and Clément~Farabet.
\newblock 2011.
\newblock Torch7: A matlab-like environment for machine learning.
\newblock {\em BigLearn, NIPS Workshop}.

\bibitem[\protect\citename{Glorot and Bengio}2010]{Glorot:10}
Xavier~Glorot and Yoshua~Bengio.
\newblock 2010.
\newblock Understanding the difficulty of training deep feedforward neural networks.
\newblock {\em International Conference on Artificial Intelligence and Statistics}.

\bibitem[\protect\citename{Socher, Bauer, Manning and Ng}2013]{Socher:13}
Richard~Socher, John~Bauer, Christopher~D. Manning and Andrew~Ng.
\newblock 2013.
\newblock Parsing with Compositional Vector Grammars.
\newblock {\em In Proceedings of the ACL conference}.

\bibitem[\protect\citename{Socher, Manning and Ng}2010]{Socher:10}
Richard~Socher, Christopher~D. Manning and Andrew~Ng.
\newblock 2010.
\newblock Learning Continuous Phrase Representations and
Syntactic Parsing with Recursive Neural Networks.
\newblock {\em Proceedings of the NIPS-2010 Deep Learning and Unsupervised Feature Learning Workshop}.
